---
title: "SCD Paper"
author: "Vishal Midya"
date: "`r Sys.Date()`"
header-includes:
   - \usepackage{multirow}
output: 
  html_document: 
    theme: readable
    highlight: tango
    df_print: kable
    fig_caption: yes
    fig_height: 5
    number_sections: yes
    toc: yes
    toc_float: 
      collapsed: false
      smooth_scroll: true
    self_contained: true
    code_folding: hide
    toc_depth: 6
---

Folder: `r getwd()`

  <script language="javascript"> 
    function toggle(num) {
      var ele = document.getElementById("toggleText" + num);
      var text = document.getElementById("displayText" + num);
      if(ele.style.display == "block") {
        ele.style.display = "none";
        text.innerHTML = "show";
      }
      else {
        ele.style.display = "block";
        text.innerHTML = "hide";
      }
   } 
  </script>

<style>
pre {
  white-space: pre !important;
  overflow-x: scroll !important;  
  overflow-y: scroll !important;
  height: auto !important;
  max-height: 80vh !important;
}
</style>


```{r setup, include=FALSE}
options(digits = 4)
knitr::opts_chunk$set(echo = TRUE,tidy=TRUE,cache=T,warning = FALSE)
options(qwraps2_markup = "markdown")
options(knitr.table.format = "latex") 
```


```{r, include=FALSE}

library(car)
library(readr)
library(lattice)
library(nlme)
library(ggplot2)
library(GGally)
library(nnet)
library(foreign)
library(biotools)
library(glmmML)
library(MASS)
library(lme4)
library(multcomp)
library(dplyr)
library(qwraps2)
library(knitr)
library(xtable)
library(kableExtra)
library(DT)
library(glmnet)
library(corrplot)
library(epiR)
library(pROC)
library(caret)
library(xgboost)

setwd("C:/Users/acer/Desktop/PennState Project/Pediatrics/Sickle Cell")

```


```{r,include=F,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

scd <- as.data.frame(read_csv("SCD_IOS_1_29_19_new.csv"))
scd$Asthma <- factor(scd$Asthma, levels = c("Yes","No"))
scd$FEV1_Signif_change <- scd$`FEV1_Significant_Change(12%)`

for(i in 1:length(scd$FEV1_Signif_change)){
  if(is.na(scd$FEV1_Signif_change[i])==F & scd$FEV1_Signif_change[i] == 2){
    scd$FEV1_Signif_change[i] <- "significant"
  }
  else if(is.na(scd$FEV1_Signif_change[i])==F & scd$FEV1_Signif_change[i] == 1){
    scd$FEV1_Signif_change[i] <- "Not_significant"
  }
}

scd$FEV1_Signif_change <- factor(scd$FEV1_Signif_change, levels = c("significant","Not_significant"))


scd$R5_Signif_change <- scd$`R5_significant_change_20%Code`

for(i in 1:length(scd$R5_Signif_change)){
  if(is.na(scd$R5_Signif_change[i])==F & scd$R5_Signif_change[i] == 2){
    scd$R5_Signif_change[i] <- "Not_significant"
  }
  else if(is.na(scd$R5_Signif_change[i])==F & scd$R5_Signif_change[i] == 1){
    scd$R5_Signif_change[i] <- "significant"
  }
}

scd$R5_Signif_change <- factor(scd$R5_Signif_change, levels = c("significant","Not_significant"))



scd$AX_Signif_change <- scd$`AX_significant_change_40%`

for(i in 1:length(scd$AX_Signif_change)){
  if(is.na(scd$AX_Signif_change[i])==F & scd$AX_Signif_change[i] == 2){
    scd$AX_Signif_change[i] <- "Not_significant"
  }
  else if(is.na(scd$AX_Signif_change[i])==F & scd$AX_Signif_change[i] == 1){
    scd$AX_Signif_change[i] <- "significant"
  }
}

scd$AX_Signif_change <- factor(scd$AX_Signif_change, levels = c("significant","Not_significant"))


scd$AX_new  <- rep(NA_real_,length(scd$AX))

for(i in 1:length(scd$AX_new)){
  if((scd$Gender[i] == "Male" | scd$Gender[i] == "male") & is.na(scd$AX[i])==F){
    scd$AX_new[i] = exp(-0.034 * scd$Height_cm[i] + 4.524)
  }
  else if(scd$Gender[i] == "Female" & is.na(scd$AX[i])==F){
    scd$AX_new[i] = exp(-0.033* scd$Height_cm[i] + 4.508)
  }
}

scd$AX_ratio <- (scd$AX/scd$AX_new)*100
scd$AX_AUC <- ((scd$Frespred * scd$X5Hzpred)/2)/100

scd$DLCO_ADJUSTED_Hb_pp <- rep(NA_real_,dim(scd)[1])

for(i in 1:dim(scd)[1]){
  if(is.na(scd$DLCO_ADJUSTED_Hb_New[i]) == F){
    scd$DLCO_ADJUSTED_Hb_pp[i] <- as.numeric(strsplit(scd$DLCO_ADJUSTED_Hb_New[i],"%")[[1]][1])
  }
}


```


# Table 4 Results

## Diagnostic Values

### FEV1

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

epi.tests(table(scd$FEV1_Signif_change,scd$Asthma))

```


### AX

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

epi.tests(table(scd$AX_Signif_change,scd$Asthma))

```


### R5

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

epi.tests(table(scd$R5_Signif_change,scd$Asthma))

```


## Test of Proportions for Table 4

### Table 4

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

table4 <- data.frame(N = c(37,37,35), Positive_response_bronchodilator = c(20,22,7),
                     percent = c(round((20/37)*100,1),round((22/37)*100,1),
                     round((7/35)*100,1)))

rownames(table4) <- c("R5HZ","AX","FEV1")

qable(table4)

```

### FEV1 vs. R5HZ

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

prop.test(c(20,54.1),c(100,100),alternative = c("less"))

```


### FEV1 vs. AX

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

prop.test(c(20,59.5),c(100,100),alternative = c("less"))

```


# Table 1 Results

## FEV1 (%)

### Mann-Whitney Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

wilcox.test(scd$FEV1pred[scd$Asthma=="Yes"],scd$FEV1pred[scd$Asthma=="No"],paired=F)

```

### Welch Two sample t Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

t.test(scd$FEV1pred[scd$Asthma=="Yes"],scd$FEV1pred[scd$Asthma=="No"],paired=F)

```


## FEV1/FVC

### Mann-Whitney Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

wilcox.test(scd$FEV1FVC[scd$Asthma=="Yes"],scd$FEV1FVC[scd$Asthma=="No"],paired=F)

```

### Welch Two sample t Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

t.test(scd$FEV1FVC[scd$Asthma=="Yes"],scd$FEV1FVC[scd$Asthma=="No"],paired=F)

```


## FEF25-75(%)

### Mann-Whitney Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

wilcox.test(scd$FEF2575pred[scd$Asthma=="Yes"],scd$FEF2575pred[scd$Asthma=="No"],paired=F)

```

### Welch Two sample t Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

t.test(scd$FEF2575pred[scd$Asthma=="Yes"],scd$FEF2575pred[scd$Asthma=="No"],paired=F)

```



## R5Hz (%)

### Mann-Whitney Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

wilcox.test(scd$R5Hzpred[scd$Asthma=="Yes"],scd$R5Hzpred[scd$Asthma=="No"],paired=F)

```

### Welch Two sample t Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

t.test(scd$R5Hzpred[scd$Asthma=="Yes"],scd$R5Hzpred[scd$Asthma=="No"],paired=F)

```



## X5Hz (%)

### Mann-Whitney Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

wilcox.test(scd$X5Hzpred[scd$Asthma=="Yes"],scd$X5Hzpred[scd$Asthma=="No"],paired=F)

```

### Welch Two sample t Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

t.test(scd$X5Hzpred[scd$Asthma=="Yes"],scd$X5Hzpred[scd$Asthma=="No"],paired=F)

```


## AX

### Mann-Whitney Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

wilcox.test(scd$AX[scd$Asthma=="Yes"],scd$AX[scd$Asthma=="No"],paired=F)

```

### Welch Two sample t Test

```{r,include=T,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

t.test(scd$AX[scd$Asthma=="Yes"],scd$AX[scd$Asthma=="No"],paired=F)

```


# ROC Curves

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

scd$AXchangeInverse <- -1* scd$AXchange
wpred <- scd[,(colnames(scd) %in% c("MRN","FEV1pred","FEV1FVC","FEF2575pred","R5Hzpred",
                                    "AX","FEV1change","FEV1FVCchange","FEF2575change",
                                    "R5changeInverse","AXchangeInverse","Asthma"))]

wpred$Asthma <- as.character(wpred$Asthma)

for(i in 1:length(wpred$Asthma)){
  if(is.na(wpred$Asthma[i])==F & wpred$Asthma[i]=="Yes"){
    wpred$Asthma[i] = 1
  }
  if(is.na(wpred$Asthma[i])==F & wpred$Asthma[i]=="No"){
    wpred$Asthma[i] = 0
  }
}

wpred$Asthma <- as.numeric(wpred$Asthma)

```


## AXchangeInverse

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_AX_chnage <- roc(wpred$Asthma,wpred$AXchangeInverse,plot = T,ci =T,percent= F,grid =T))

```

## FEV1change

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_FEV1_change <- roc(wpred$Asthma,wpred$FEV1change,plot = T,ci =T,percent= F,grid =T))

```

## R5changeInverse

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_R5_change <- roc(wpred$Asthma,wpred$R5changeInverse,plot = T,ci =T,percent= F,grid =T))

```

## FEF2575change

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_FEF2575_change <- roc(wpred$Asthma,wpred$FEF2575change,plot = T,ci =T,percent= F,grid =T))

```

## FEV1FVCchange

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_FEV1FVC_change <- roc(wpred$Asthma,wpred$FEV1FVCchange,plot = T,ci =T,percent= F,grid =T))

```

## FEV1pred

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_FEV1_pred <- roc(wpred$Asthma,wpred$FEV1pred,plot = T,ci =T,percent= F,grid =T))

```

## FEV1FVC

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_FEV1FVC <- roc(wpred$Asthma,wpred$FEV1FVC,plot = T,ci =T,percent= F,grid =T))

```

## FEF2575pred

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_FEF2575pred <- roc(wpred$Asthma,wpred$FEF2575pred,plot = T,ci =T,percent= F,grid =T))

```

## R5Hzpred

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_R5Hzpred <- roc(wpred$Asthma,wpred$R5Hzpred,plot = T,ci =T,percent= F,grid =T))

```

## AX

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

(roc_AX <- roc(wpred$Asthma,wpred$AX,plot = T,ci =T,percent= F,grid =T))

```


### Ranking Based on Youden Statistic

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

roc_table <- data.frame(Names = c("AXchangeInverse","FEV1change","R5changeInverse","FEF2575change","FEV1FVCchange","FEV1pred","FEV1FVC","FEF2575pred","R5Hzpred","AX"),
                        AUC = c(as.numeric(roc_AX_chnage$auc),as.numeric(roc_FEV1_change$auc),as.numeric(roc_R5_change$auc), as.numeric(roc_FEF2575_change$auc),as.numeric(roc_FEV1FVC_change$auc),as.numeric(roc_FEV1_pred$auc),as.numeric(roc_FEV1FVC$auc),as.numeric(roc_FEF2575pred$auc),as.numeric(roc_R5Hzpred$auc),as.numeric(roc_AX$auc)),
                        AUC_CI =
                          c(paste0(round(as.numeric(roc_AX_chnage$ci)[1],2),"-",round(as.numeric(roc_AX_chnage$ci)[2],2)),
                            paste0(round(as.numeric(roc_FEV1_change$ci)[1],2),"-",round(as.numeric(roc_FEV1_change$ci)[2],2)),paste0(round(as.numeric(roc_R5_change$ci)[1],2),"-",round(as.numeric(roc_R5_change$ci)[2],2)),
                            paste0(round(as.numeric(roc_FEF2575_change$ci)[1],2),"-",round(as.numeric(roc_FEF2575_change$ci)[2],2)),
                            paste0(round(as.numeric(roc_FEV1FVC_change$ci)[1],2),"-",round(as.numeric(roc_FEV1FVC_change$ci)[2],2)),
                            paste0(round(as.numeric(roc_FEV1_pred$ci)[1],2),"-",round(as.numeric(roc_FEV1_pred$ci)[2],2)),
                            paste0(round(as.numeric(roc_FEV1FVC$ci)[1],2),"-",round(as.numeric(roc_FEV1FVC$ci)[2],2)),
                            paste0(round(as.numeric(roc_FEF2575pred$ci)[1],2),"-",round(as.numeric(roc_FEF2575pred$ci)[2],2)),
                            paste0(round(as.numeric(roc_R5Hzpred$ci)[1],2),"-",round(as.numeric(roc_R5Hzpred$ci)[2],2)),
                            paste0(round(as.numeric(roc_AX$ci)[1],2),"-",round(as.numeric(roc_AX$ci)[2],2))))


roc_table$Optimal_specificity = c(as.numeric(coords(roc_AX_chnage,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_FEV1_change,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_R5_change ,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_FEF2575_change,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_FEV1FVC_change,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_FEV1_pred,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_FEV1FVC,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_FEF2575pred ,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_R5Hzpred ,x="best",as.list=F, best.method=c("youden"))[2]),as.numeric(coords(roc_AX  ,x="best",as.list=F, best.method=c("youden"))[2]))

roc_table$Optimal_sensitivity = c(as.numeric(coords(roc_AX_chnage,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_FEV1_change,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_R5_change ,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_FEF2575_change,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_FEV1FVC_change,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_FEV1_pred,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_FEV1FVC,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_FEF2575pred ,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_R5Hzpred ,x="best",as.list=F, best.method=c("youden"))[3]),as.numeric(coords(roc_AX  ,x="best",as.list=F, best.method=c("youden"))[3]))

roc_table$Youden_statistic <- (roc_table$Optimal_specificity + roc_table$Optimal_sensitivity - 1)

qable(roc_table[order(roc_table$Youden_statistic,decreasing = T),])

```


# XGBoost

```{r,include=F,tidy=TRUE,echo=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

scd$AXchangeInverse <- -1* scd$AXchange
wpred <- scd[,(colnames(scd) %in% c("MRN","FEV1pred","FEV1FVC","FEF2575pred","R5Hzpred",
                                    "AX","FEV1change","FEV1FVCchange","FEF2575change",                            "R5changeInverse","AXchangeInverse","Asthma"))]

wpred$Asthma <- as.character(wpred$Asthma)

for(i in 1:length(wpred$Asthma)){
  if(is.na(wpred$Asthma[i])==F & wpred$Asthma[i]=="Yes"){
    wpred$Asthma[i] = 1
  }
  if(is.na(wpred$Asthma[i])==F & wpred$Asthma[i]=="No"){
    wpred$Asthma[i] = 0
  }
}

wpred$Asthma <- as.numeric(wpred$Asthma)

train = sample(wpred$MRN,ceiling((dim(wpred)[1])*100/100))

test = wpred$MRN[!(wpred$MRN %in% train)]

x_train= data.matrix(wpred[wpred$MRN %in% train,!(colnames(wpred) %in% 
                                                    c("MRN","Asthma"))])

y_train = data.matrix(wpred[wpred$MRN %in% train,c("Asthma")])

x_test = data.matrix(wpred[(wpred$MRN %in% test),!(colnames(wpred) %in% 
                                                     c("MRN","Asthma"))])

y_test = data.matrix(wpred[wpred$MRN %in% test,c("Asthma")])

```

## Model


```{r,include=T,tidy=TRUE,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

set.seed(9294)
xgb <-xgboost(data = x_train, label = y_train, 
              nrounds = 50, prediction = T,
              nfold = 3,verbose = T,maximize=FALSE,
              objective = "reg:logistic",eval_metric = "error", booster = "gbtree",
              max_depth = 8, eta = 0.06564606, gamma = 0.144125, subsample = 0.7176255,
              colsample_bytree = 0.7405726, min_child_weight = 3,
              max_delta_step = 5, nthread=6)

imp <- xgb.importance(model = xgb)
imp <- as.data.frame(imp)

```

## Variable Importance

### Gain

```{r,include=T,tidy=TRUE,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

qable(imp[order(imp$Gain, decreasing = T),c("Feature","Gain")])

```

### Frequency

```{r,include=T,tidy=TRUE,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

qable(imp[order(imp$Frequency, decreasing = T),c("Feature","Frequency")])

```


### Cover

```{r,include=T,tidy=TRUE,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

qable(imp[order(imp$Cover, decreasing = T),c("Feature","Cover")])

```


# ANN

```{r,include=T,tidy=TRUE,echo=T,eval=F,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

scd$AXchangeInverse <- -1* scd$AXchange
wpred <- scd[,(colnames(scd) %in% c("MRN","FEV1pred","FEV1FVC","FEF2575pred","R5Hzpred",
                                    "AX","FEV1change","FEV1FVCchange","FEF2575change",                            "R5changeInverse","AXchangeInverse","Asthma"))]

wpred$Asthma <- as.character(wpred$Asthma)

for(i in 1:length(wpred$Asthma)){
  if(is.na(wpred$Asthma[i])==F & wpred$Asthma[i]=="Yes"){
    wpred$Asthma[i] = 1
  }
  if(is.na(wpred$Asthma[i])==F & wpred$Asthma[i]=="No"){
    wpred$Asthma[i] = 0
  }
}

wpred$Asthma <- as.numeric(wpred$Asthma)
wpred$Asthma <- factor(wpred$Asthma)

train = sample(wpred$MRN,ceiling((dim(wpred)[1])*100/100))

test = wpred$MRN[!(wpred$MRN %in% train)]

x_train= data.matrix(wpred[wpred$MRN %in% train,!(colnames(wpred) %in% 
                                                    c("MRN","Asthma"))])

y_train = data.matrix(wpred[wpred$MRN %in% train,c("Asthma")])

x_test = data.matrix(wpred[(wpred$MRN %in% test),!(colnames(wpred) %in% 
                                                     c("MRN","Asthma"))])

y_test = data.matrix(wpred[wpred$MRN %in% test,c("Asthma")])

library(h2o)

h2o.init(nthreads=-1, max_mem_size="20G")

x_train_deep = as.data.frame(data.matrix(wpred[wpred$MRN %in% train,!(colnames(wpred) %in% 
                                                                        c("MRN","Asthma"))]))
x_train_deep$y <- wpred$Asthma
x_train.hex <- as.h2o(x_train_deep)



best_seednumber = 1234
best_test_error_mean = 2
best_test_error_std = NA_real_
best_param = list()

for (iter in 1:100) {
  
  seed.number = sample.int(10000, 1)[[1]]
  set.seed(seed.number)
  
  hyper_params <- list(
    activation=sample(c("Tanh","TanhWithDropout"),1),
    input_dropout_ratio=runif(1,0,0.05),
    l1=sample(seq(0,1e-4,1e-6),1),
    l2=sample(seq(0,1e-4,1e-6),1))
  
  h2o.dl.3 <- h2o.deeplearning(x=1:dim(x_train.hex)[2]-1, y= dim(x_train.hex)[2], 
                               training_frame = x_train.hex, nfolds = 3,
                                ignore_const_cols =F, seed =  seed.number, reproducible = T,
                                keep_cross_validation_predictions =T,loss = "Automatic",
                                hidden = c(200,200), fold_assignment = "Modulo",
                               stopping_metric = "misclassification", 
                               activation = hyper_params$activation,
                               input_dropout_ratio = hyper_params$input_dropout_ratio,
                                l1=hyper_params$l1, l2=hyper_params$l2, 
                                missing_values_handling = "MeanImputation")
  
  min_test_error_mean = as.numeric(h2o.dl.3@model$ cross_validation_metrics_summary["err","mean"])
  min_test_error_std = as.numeric(h2o.dl.3@model$ cross_validation_metrics_summary["err","sd"])
  
  if (min_test_error_mean < best_test_error_mean) {
    
    best_test_error_mean = min_test_error_mean
    best_test_error_std = min_test_error_std
    best_seednumber = seed.number
    
    best_param =  hyper_params
  }
}

best_test_error_mean    
best_test_error_std     
best_seednumber 
best_param

seed.number = 1375
h2o.dl.3 <- h2o.deeplearning(x=1:dim(x_train.hex)[2]-1, y= dim(x_train.hex)[2],
                              training_frame = x_train.hex,nfolds = 3,
                             ignore_const_cols =F, seed =  seed.number, reproducible = T,
                             keep_cross_validation_predictions =T,loss = "Automatic",
                             hidden = c(200,200), fold_assignment = "Modulo",
                             stopping_metric = "misclassification", 
                             activation = "Tanh",
                             input_dropout_ratio = 0.001742793 ,
                             l1= 7.8e-05, l2 = 4.5e-05 , 
                             missing_values_handling = "MeanImputation")

(as.data.frame(h2o.varimp(h2o.dl.3)))


```


## Variable Importance

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

ANN <- data.frame(variable = c("R5Hzpred","FEV1FVCchange","FEV1FVC","AXchangeInverse",
                               "AX","R5changeInverse","FEF2575pred","FEF2575change",
                               "FEV1pred","FEV1change"),
                  relative_importance = c(1,0.9215299,0.9174837,0.8997086,
                                          0.8970649,0.8946820,0.8766919,
                                          0.8759320,0.8593777,0.8480096),
                  percentage = c(0.11122876,0.10250063,0.10205058,
                                 0.10007348,0.09977941,0.09951437,
                                 0.09751335,0.09742883,0.09558752,0.09432306))
qable(ANN)


```


# Robust Linear Regressions: Between Height and PFT vs. Height and IOS measures

## IOS Measures

### Frespred

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

library(robust)

w_Frespred <- lmRob((Frespred) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_Frespred)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.Frespred.rlm <- rlm((Frespred) ~ Height_cm ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.Frespred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting_IOS

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.Frespred.rlm <- rlm((Frespred) ~ Ageattesting_IOS ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.Frespred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


### X5Hzpred

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_X5Hzpred <- lmRob((X5Hzpred) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_X5Hzpred)

```


#### Height_cm


```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.X5Hzpred.rlm <- rlm((X5Hzpred) ~ Height_cm + BT_2years +hospitalization ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.X5Hzpred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting_IOS

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.X5Hzpred.rlm <- rlm((X5Hzpred) ~ Ageattesting_IOS + BT_2years +hospitalization  ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.X5Hzpred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


### R5Hzpred

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_R5Hzpred <- lmRob((R5Hzpred) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_R5Hzpred)

```

#### Height_cm
                      
```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.R5Hzpred.rlm <- rlm((R5Hzpred) ~ Height_cm   ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.R5Hzpred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting_IOS

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.R5Hzpred.rlm <- rlm((R5Hzpred) ~ Ageattesting_IOS  ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.R5Hzpred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


## PFT Measures

### FEV1pred

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_FEV1pred <- lmRob((FEV1pred) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_FEV1pred)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.FEV1pred.rlm <- rlm((FEV1pred) ~ Height_cm + Years_hydroxyurea,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.FEV1pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.FEV1pred.rlm <- rlm((FEV1pred) ~ Ageattesting + Years_hydroxyurea ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.FEV1pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


### FEV1FVC

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_FEV1FVC <- lmRob((FEV1FVC) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_FEV1FVC)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.FEV1FVC.rlm <- rlm((FEV1FVC) ~ Height_cm ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.FEV1FVC.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.FEV1FVC.rlm <- rlm((FEV1FVC) ~ Ageattesting ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.FEV1FVC.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


### FEF2575pred

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_FEF2575pred <- lmRob((FEF2575pred) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_FEF2575pred)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.FEF2575pred.rlm <- rlm((FEF2575pred) ~ Height_cm ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.FEF2575pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.FEF2575pred.rlm <- rlm((FEF2575pred) ~ Ageattesting ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.FEF2575pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


## TLCpred

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_TLCpred <- lmRob((TLCpred) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_TLCpred)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.TLCpred.rlm <- rlm((TLCpred) ~ Height_cm + LDH + Years_hydroxyurea + BT_2years 
                      +hospitalization+  Reticulocyte_Count +SpO2
                     ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.TLCpred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.TLCpred.rlm <- rlm((TLCpred) ~ Ageattesting +  LDH + Years_hydroxyurea + BT_2years 
                      +hospitalization+  Reticulocyte_Count +SpO2 ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.TLCpred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


## DLCO_Hb_VA_corrected

### Plot for DLCO_Hb_VA_corrected vs. Height

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

plot(scd$Height_cm,scd$DLCO_Hb_VA_corrected, xlab= "Height", ylab = "DLCO_Hb_VA_corrected")

```

### Plot for DLCO_Hb_VA_corrected vs. Age

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

plot(scd$Ageattesting,scd$DLCO_Hb_VA_corrected, xlab= "Age", ylab = "DLCO_Hb_VA_corrected")

```

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_DLCO_Hb_VA_corrected <- lmRob((DLCO_Hb_VA_corrected) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_DLCO_Hb_VA_corrected)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.DLCO_Hb_VA_corrected.rlm <- rlm((DLCO_Hb_VA_corrected) ~ Height_cm + Years_hydroxyurea +
                                    hospitalization+ Reticulocyte_Count + SpO2,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.DLCO_Hb_VA_corrected.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting_IOS

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.DLCO_Hb_VA_corrected.rlm <- rlm((DLCO_Hb_VA_corrected) ~ Ageattesting_IOS + Years_hydroxyurea  +hospitalization+ Reticulocyte_Count + SpO2,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.DLCO_Hb_VA_corrected.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```



## DLCO_ADJUSTED_Hb_pp

### Plot for DLCO_ADJUSTED_Hb_pp vs. Height

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

plot(scd$Height_cm,scd$DLCO_ADJUSTED_Hb_pp, xlab= "Height", ylab = "DLCO_ADJUSTED_Hb_pp")

```

### Plot for DLCO_ADJUSTED_Hb_pp vs. Age

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

plot(scd$Ageattesting,scd$DLCO_ADJUSTED_Hb_pp, xlab= "Age", ylab = "DLCO_ADJUSTED_Hb_pp")

```

#### Other Predictor

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

w_DLCO_ADJUSTED_Hb_pp <- lmRob((DLCO_ADJUSTED_Hb_pp) ~ LDH + Years_hydroxyurea + BT_2years+ ACS_2years
                      +hospitalization+ HbF + Reticulocyte_Count +SpO2,data=scd)

summary(w_DLCO_ADJUSTED_Hb_pp)

```


#### Height_cm

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.DLCO_ADJUSTED_Hb_pp.rlm <- rlm((DLCO_ADJUSTED_Hb_pp) ~ Height_cm ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.DLCO_ADJUSTED_Hb_pp.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

#### Ageattesting_IOS

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.DLCO_ADJUSTED_Hb_pp.rlm <- rlm((DLCO_ADJUSTED_Hb_pp) ~ Ageattesting_IOS ,data=scd,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.DLCO_ADJUSTED_Hb_pp.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


# Robust Regression for Controls

## R5Hz_pred

### Height

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

control <- as.data.frame(read_csv("SCD_IOS_Control_12_8_18_Alison.csv"))

f.R5Hz_pred.rlm <- rlm(R5Hz_pred ~ Height ,data=control,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.R5Hz_pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

### Age

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.R5Hz_pred.rlm <- rlm(R5Hz_pred ~ Age ,data=control,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.R5Hz_pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


## X5Hz_pred

### Height

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.X5Hz_pred.rlm <- rlm(X5Hz_pred ~ Height ,data=control,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.X5Hz_pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

### Age

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.X5Hz_pred.rlm <- rlm(X5Hz_pred ~ Age ,data=control,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.X5Hz_pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```


## Fres_pred

### Height

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.Fres_pred.rlm <- rlm(Fres_pred ~ Height ,data=control,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.Fres_pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

### Age

```{r,include=T,tidy=T,eval=T,echo=T,strip.white=TRUE,highlight=TRUE,fig.align='center',dpi=200}

f.Fres_pred.rlm <- rlm(Fres_pred ~ Age ,data=control,
               maxit=1e3,psi=psi.hampel, method = "M", scale.est="proposal 2")

surmod=summary(f.Fres_pred.rlm)
dd=data.frame(surmod$coefficients)
dd$p.value=2*pt(abs(dd$t.value), surmod$df[2], lower.tail=FALSE) 
qable(round(dd,5))

```

